Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-02 paper/galsize_paper.tex
Added discussion of Figure 8

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/blue_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/red_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/disk_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/bulge_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\caption{
{\bf Distinct $\rhalf-$dependence of clustering for color- or morphology-selected galaxy samples.}
All panels show the clustering of galaxies in the same bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ In the {\em upper left} panel, we first select blue galaxies based on $g-r<0.6,$ and subsequently compute $\median{\rhalf}{\mstar}$ {\em of the color-selected sample}. This results in identical stellar mass function for large and small blue galaxy samples, in analogy to the left panel of Figure \ref{fig:sizedefinition}. The {\em upper right panel} shows results of the same procedure for ``red" galaxies, defined by $g-r>0.6.$ The top two panels show that for color-selected samples, the magnitude of the $\rhalf-$dependence of clustering is dramatically reduced, and changes sign, relative to $\mstar-$complete samples. Using the \citet{meert_etal15} measurements of the disk/bulge decomposition of the 2d $r-$band luminosity profile $L_{\rm r},$ the bottom left panel shows analogous results for disk-dominated galaxies defined by $L_{\rm r}^{\rm bulge}<L_{\rm r}^{\rm tot}/4;$ the bottom right panel shows results for bulge-dominated galaxies defined by $L_{\rm r}^{\rm disk}<L_{\rm r}^{\rm tot}/4.$
}
\label{fig:strippingorphans}
\end{figure*}
%---------------------------------------------------------------------------------------------------

>>>>

In this section we take a preliminary look at how galaxy clustering exhibits simultaneous dependence upon broadband color, morphology, and size. Beginning from the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples according to a $g-r=0.65$ cut, the rough location of the trough of the green valley for this stellar mass. For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size values to split each subsample into two.

In the top left panel of Figure \ref{fig:colorclustering} we show the clustering of large vs. small red galaxies; in the top right panel we show the same for blue galaxies. For each color-selected sample, large galaxies are slightly more strongly clustered relative to small galaxies. Comparing the top panels of Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the dramatic impact of galaxy color selection upon $\rhalf-$dependent clustering. For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, and the magnitude of the effect weakens considerably.

The bottom panels of Figure \ref{fig:colorclustering} show results that are analogous to the top panels, but instead using of $g-r$ color, we first divide the $\mstar>10^{10.25}\msun$ sample into ``bulge-dominated" and ``disk-dominated" sequences according to $B/T,$ the fraction of $r-$band flux coming from the bulge component of the 2d light profile measurements in the \citet{meert_etal15} catalog. We define a galaxy as bulge-dominated if $B/T<0.25,$ and disk-dominated if $B/T>0.75.$ We separately split the disk-dominated and bulge-dominated subsample into two based on the median size $\median{\rhalf}{\mstar;B/T}$ appropriate for each subsample. The bottom left panel of Figure \ref{fig:colorclustering} compares the clustering of small vs. large disk-dominated galaxies; the bottom right panel shows the same comparison for bulge-dominated galaxies.

The contrast between the two bottom panels is stark. The clustering of large vs. small bulge-dominated galaxies has almost no dependence upon $\rhalf.$ On the other hand, for disk-dominated galaxies, small galaxies are much more strongly clustered, and the effect is strong. In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.

A proper interpretation of these results requires forward-modeling the joint dependence of the galaxy-halo connection upon $\mstar, \rhalf, g-r, $ and $B/T,$ which is beyond the scope of this work (though see \S\ref{subsec:future} for discussion of future work). Nonetheless, the broad features of these clustering signals give insight into the characteristics that any model for these properties should exhibit. The clustering trends of bulge-dominated galaxies indicates that the size of the bulge is likely to have only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} On the other hand, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that the size of disk-dominated galaxies is strongly correlated with whether or not the galaxy is a satellite. We elaborate upon this halo model interpretation in \S\ref{subsec:future}.

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/blue_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/red_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/disk_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\includegraphics[width=8cm]{FIGS/bulge_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
\caption{
{\bf Distinct $\rhalf-$dependence of clustering for color- or morphology-selected galaxy samples.}
All panels show the clustering of galaxies in the same bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ In the {\em upper left} panel, we first select blue galaxies based on $g-r<0.6,$ and subsequently compute $\median{\rhalf}{\mstar}$ {\em of the color-selected sample}. This results in identical stellar mass function for large and small blue galaxy samples, in analogy to the left panel of Figure \ref{fig:sizedefinition}. The {\em upper right panel} shows results of the same procedure for ``red" galaxies, defined by $g-r>0.6.$ The top two panels show that for color-selected samples, the magnitude of the $\rhalf-$dependence of clustering is dramatically reduced, and changes sign, relative to $\mstar-$complete samples. Using the \citet{meert_etal15} measurements of the disk/bulge decomposition of the 2d $r-$band luminosity profile $L_{\rm r},$ the bottom left panel shows analogous results for disk-dominated galaxies defined by $L_{\rm r}^{\rm bulge}<L_{\rm r}^{\rm tot}/4;$ the bottom right panel shows results for bulge-dominated galaxies defined by $L_{\rm r}^{\rm disk}<L_{\rm r}^{\rm tot}/4.$
}
\label{fig:colorclustering}
\end{figure*}
%---------------------------------------------------------------------------------------------------
